A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-14 paper/paper.tex
Changed plot sizes, removed a couple of plots

Experiments were performed on a cluster of machines with Dual Xeon E5-2640
v2 CPUs and 64GBytes RAM. 
%Parallel experiments used 32 threads per machine,
%using all 16 physical cores with hyper-threading enabled.
All experiments used a database of
randomly-generated Maximum Common Subgraph instances, which contains graphs of
order ranging from 10 to 100 vertices
\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}.  For
unlabelled instances, we selected 10 per cent of the 41,100 instances with up
to 40 vertices; labels were discarded. For labelled instances, we selected 10
per cent of the full database of 81,400 instances, and used a labelling scheme
in which the number of distinct vertex labels and the number of distinct edge
labels is approximately equal to 33 per cent of the number of vertices in each
graph.
Small scale experiments (not presented here) were performed to identify a suitable heuristic for label class selection. The heuristic used selects the label class  with the smallest product $|P| \times |T|$ (a surrogate for expected branching factor) and from that selects the first vertex in $P$.

@@

\paragraph{Vertex labels, no edge labels, undirected} are in \cref{figure:33v-cumulative}, and are not in other papers so we should omit this unless we see something interesting.

\paragraph{Vertex labels,  edge labels, undirected} are in \cref{figure:33ve-cumulative}, and are not in other papers so we should omit this unless we see something interesting.

@@

\paragraph{Compared to CP FC} Nodes are in \cref{figure:plain-james-versus-cp-fc-nodes-scatter} and \cref{figure:33ved-james-versus-cp-fc-nodes-scatter}.

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33v-cumulative.pdf}
    \caption{MCS 33\% vertex labelled, no edge labels, undirected instances, cumulative runtimes}\label{figure:33v-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ve-cumulative.pdf}
    \caption{MCS 33\% vertex and edge labelled undirected instances, cumulative runtimes}\label{figure:33ve-cumulative}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Nodes (TODO?? heatmapify this
    and exclude timeouts)}\label{figure:plain-james-versus-cp-fc-nodes-scatter}
\end{figure}

>>>>

Experiments were performed on a cluster of machines with Dual Xeon E5-2640
v2 CPUs and 64GBytes RAM. 
%Parallel experiments used 32 threads per machine,
%using all 16 physical cores with hyper-threading enabled.
All experiments used a database of
randomly-generated Maximum Common Subgraph instances, which contains graphs of
order ranging from 10 to 100 vertices
\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}.  For
unlabelled instances, we selected 10 per cent of the 41,100 instances with up
to 40 vertices; labels were discarded. For labelled instances, we selected 10
per cent of the full database of 81,400 instances, and used a labelling scheme
in which the number of distinct vertex labels and the number of distinct edge
labels is approximately equal to 33 per cent of the number of vertices in each
graph.

Small scale experiments (not presented here) were performed to identify a
suitable heuristic for label class selection. The heuristic used selects the
label class  with the smallest $\min(|P|,|T|)$ (a surrogate for expected
branching factor). From this class, a vertex is selected from $P$ with maximum
degree if $H$ is sparse and with minimum degree if $H$ is dense.

@@

\paragraph{Vertex labels, no edge labels, undirected} are in
FIGURE REMOVED
%\cref{figure:33v-cumulative},
and are not in other papers so we should omit this unless we see something interesting.

\paragraph{Vertex labels,  edge labels, undirected} are in
FIGURE REMOVED
%\cref{figure:33ve-cumulative},
and are not in other papers so we should omit this unless we see something interesting.

@@

\paragraph{Compared to CP FC} Nodes are in
FIGURE REMOVED
%\cref{figure:plain-james-versus-cp-fc-nodes-scatter}
and \cref{figure:33ved-james-versus-cp-fc-nodes-scatter}.

@@

%\begin{figure}
%    \centering
%    \includegraphics*{gen-graph-33v-cumulative.pdf}
%    \caption{MCS 33\% vertex labelled, no edge labels, undirected instances, cumulative runtimes}\label{figure:33v-cumulative}
%\end{figure}
%
%\begin{figure}
%    \centering
%    \includegraphics*{gen-graph-33ve-cumulative.pdf}
%    \caption{MCS 33\% vertex and edge labelled undirected instances, cumulative runtimes}\label{figure:33ve-cumulative}
%\end{figure}

@@

%\begin{figure}
%    \centering
%    \includegraphics*{gen-graph-plain-james-versus-cp-fc-nodes-scatter.pdf}
%    \caption{MCS Plain instances, James vs CP-FC, Nodes (TODO?? heatmapify this
%    and exclude timeouts)}\label{figure:plain-james-versus-cp-fc-nodes-scatter}
%\end{figure}
